Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-27 Paper/Figures.Rnw
Changed map to refer to county population

    ggplot(map.df, aes(x=long, y=lat)) +
        theme_light(base_size=plotTextBaseSize) +
        scale_fill_manual(labels=legendLabels(c("$<$50", "$>$100")), values=c(lightBlue, darkBlue)) +
        geom_polygon(aes(fill=highRSV, group=group), color="white", size=.5) +
        geom_text(data=county.data, aes(label=name), size=2.2) +
        coord_map() + 
        labs(fill="Average RSV-associated hospitalizations per year") +
        theme(
            rect=element_blank(),
            line=element_blank(),
            axis.text=element_blank(),
            axis.title=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@

>>>>

    ggplot(map.df, aes(x=long, y=lat)) +
        theme_light(base_size=plotTextBaseSize) +
        scale_fill_manual(labels=legendLabels(c("$<300,000$", "$>900,000$")), values=c(lightBlue, darkBlue)) +
        geom_polygon(aes(fill=highRSV, group=group), color="white", size=.5) +
        geom_text(data=county.data, aes(label=name), size=2.2) +
        coord_map() + 
        labs(fill="Total county population in 2010 census") +
        theme(
            rect=element_blank(),
            line=element_blank(),
            axis.text=element_blank(),
            axis.title=element_blank(),
            legend.position="bottom"
        )
    dev.off()
@
